Data preparation

### 2023-12-07 procesamiento/01-prod_prep-micro.Rmd
code

# Perceived integration

```{r}
#frq(df1$v31)
df1$pi_compa <- car::recode(df1$v31,recodes = "c(0,8,9)=NA")
df1$pi_compa <- set_na(df1$pi_compa,na = c(0,8,9))
# df1$pi_compa <- sjmisc::rec(x = df1$pi_compa,rec = "rev")
sjlabelled::set_label(df1$pi_compa) <- "Perceived integration: companionship lacking"
#frq(df1$pi_compa)

#frq(df1$v32)
df1$pi_isola <- car::recode(df1$v32,recodes = "c(0,8,9)=NA")
df1$pi_isola <- set_na(df1$pi_isola,na = c(0,8,9))
# df1$pi_isola <- sjmisc::rec(x = df1$pi_isola,rec = "rev")
sjlabelled::set_label(df1$pi_isola) <- "Perceived integration: isolated from others"
#frq(df1$pi_compa)

#frq(df1$v33)
df1$pi_left <- car::recode(df1$v33,recodes = "c(0,8,9)=NA")
df1$pi_left <- set_na(df1$pi_left,na = c(0,8,9))
# df1$pi_left <- sjmisc::rec(x = df1$pi_left,rec = "rev")
sjlabelled::set_label(df1$pi_left) <- "Perceived integration: left out from activities"
#frq(df1$pi_left)

df1$isolation<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
sjlabelled::set_label(df1$isolation) <- "Perceived isolation"
```

# Trust

```{r}
df1$tr_inte <- car::recode(df1$v35,recodes = "c(0,8,9)=NA")
df1$tr_inte <- set_na(df1$tr_inte,na = c(0,8,9))
df1$tr_inte <- sjmisc::rec(x = df1$tr_inte,rec = "rev")
sjlabelled::set_label(df1$tr_inte) <- "Interpersonal trust"
frq(df1$tr_inte)

df1$tr_courts <- car::recode(df1$v36,recodes = "c(98,99)=NA")
df1$tr_courts <- set_na(df1$tr_courts,na = c(98,99))
# df1$tr_courts <- sjmisc::rec(x = df1$tr_courts,rec = "rev")
sjlabelled::set_label(df1$tr_courts) <- "Trust in courts"
frq(df1$tr_courts)
```

@@

```{r class-from-stata}
# Load the data created in stata------------------------------------------------
df_class <- haven::read_dta(file = here::here("input/data/proc/class_respondent-spouse.dta"))
df1 <- left_join(df1,df_class,by='id')

@@

# Community participation

```{r}
# frq(df1$v17)
df1$act_lei <- car::recode(df1$v17,recodes = "c(0,8,9)=NA")
df1$act_lei <- set_na(df1$act_lei,na = c(0,8,9))
df1$act_lei <- sjmisc::rec(x = df1$act_lei,rec = "rev")
sjlabelled::set_label(df1$act_lei) <- "Activities: groups for leisure, sports or culture"
# frq(df1$act_lei)

# frq(df1$v18)
df1$act_pol <- car::recode(df1$v18,recodes = "c(0,8,9)=NA")
df1$act_pol <- set_na(df1$act_pol,na = c(0,8,9))
df1$act_pol <- sjmisc::rec(x = df1$act_pol,rec = "rev")
sjlabelled::set_label(df1$act_pol) <- "Activities: political parties, groups, associations"
# frq(df1$act_pol)

# frq(df1$v19)
df1$act_vol <- car::recode(df1$v19,recodes = "c(0,8,9)=NA")
df1$act_vol <- set_na(df1$act_vol,na = c(0,8,9))
df1$act_vol <- sjmisc::rec(x = df1$act_vol,rec = "rev")
sjlabelled::set_label(df1$act_vol) <- "Activities: charitable or religious - voluntary"
# frq(df1$act_vol)

# cor(df1[,c("act_lei","act_pol","act_vol")],use="complete.obs")
# psych::alpha(df1[,c("act_lei","act_pol","act_vol")])

df1$activities<- rowMeans(df1[,c("act_lei","act_pol","act_vol")],na.rm = T)
sjlabelled::set_label(df1$activities) <- "Participation in social activities"
# summary(df1$activities)
```

>>>>

@@

```{r class-from-stata1}
# Load the data created in stata------------------------------------------------
df_class <- haven::read_dta(file = here::here("input/data/proc/class_respondent-spouse.dta"))
df1 <- left_join(df1,df_class,by='id')

@@
